Paper 3 - Causal Roadmap

### 2023-03-24 docs/causal_roadmap.qmd
Switched to myphd R package for DAGs. Started working on DAG for RQ3

    - We will use MR-Egger [@BowdenDaveySmithBurgess:2015], weighted median [@BowdenSmithHaycock:2016], and MR-PRESSO [@VerbanckChenNeale:2018] for sensitivity analyses. For *secondary* sensitivity analyses, we will use: Steiger filtering, Cochran's Q-statistics (to check for heterogeneity), and the Egger intercept (to check for horizontal pleiotropy) \textcolor{red}{(citations needed)}.

@@

@@

```{r}
#| fig-cap: DAG for research question 1.
#| fig-align: center
#| fig-width: 30
#| fig-height: 40
#| out-extra: "keepaspectratio=true"
dag_rq <- dags$chem_to_out

myphd::visualize_dag(dag_rq)
# dag_rq %>%
#   ggdag::tidy_dagitty() %>%
#   ggdag::node_status() %>%
#   ggplot2::ggplot(ggplot2::aes(x, y, 
#                                xend = xend, yend = yend, 
#                                color = status)) +
#   ggdag::geom_dag_edges() +
#   ggdag::geom_dag_point() +
#   geom_dag_text_repel() +
#   ggokabeito::scale_color_okabe_ito(na.value = "grey90") +
#   theme_dag() +
#   ggplot2::coord_cartesian(clip = "off")

adj_sets <- dagitty::adjustmentSets(x = dag_rq, 
                                    type = type_mas, effect = type_effect)
```

>>>>

    - We will use MR-Egger [@BowdenDaveySmithBurgess:2015], weighted median [@BowdenSmithHaycock:2016], and MR-PRESSO [@VerbanckChenNeale:2018] for sensitivity analyses. For *secondary* sensitivity analyses, we will use: Steiger filtering and/or bi-directional \acr{mr}, Cochran's Q-statistics (to check for heterogeneity), and the Egger intercept (to check for horizontal pleiotropy [^1]) \textcolor{red}{(citations needed)}.

    [^1]: In order to address the issue of horizontal pleiotropy, and to study the joint effects of multiple traits, another possibility is represented by the use of univariable \acr{mr} for screening purposes, followed by multivariable (with clumping for \acr{ld}) \acr{mr} [@DecinaHopkinsBowden:2023].

@@

  From the metabolomics dataset, we will remove derived ratios and composite measures, and we will consider only the total lipids of each subclass [@DecinaHopkinsBowden:2023]. Among the remaining metabolomic features, we will check their genetic correlation.

@@

```{r}
#| fig-cap: DAG for research question 1.
#| fig-align: center
#| fig-width: 30
#| fig-height: 40
#| out-extra: "keepaspectratio=true"
dag_rq <- dags$chem_to_out
myphd::visualize_dag(dag_rq)
adj_sets <- dagitty::adjustmentSets(x = dag_rq, 
                                    type = type_mas, effect = type_effect)
```
